---
title: "Chapter 16"
author: "Paul"
date: '`r format(Sys.Date(), "%d\\. %m\\. %Y")`'
output: 
  html_document:
    toc: true
    toc_float: true
    number_sections: true
    df_print: paged
    code_folding: hide
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, cache = TRUE)
extrafont::loadfonts(device = "win")
windowsFonts("Arial_Narrow" = windowsFont("Arial Narrow"))
options(mc.cores = parallel::detectCores())
library(tidyverse)
theme_set(hrbrthemes::theme_ipsum(base_family = "Arial_Narrow"))
```

```{r}
library(rstan)
```
The le evaluation_discoveries.csv contains data on the numbers of \great" inventions and
scientic discoveries (Xt) in each year from 1860 to 1959 [1]. In this question you will develop a
model to explain the variation in scientic inventions over time. The simplest model here is to
assume that (a.) one discovery is independent of all others, and (b.) the rate of occurrence of
discoveries is the same in all years (). Since the data is discrete, these assumptions suggest the
use a Poisson likelihood,

# Load data
```{r}
df <- rio::import(here::here("data", "evaluation_discoveries.csv"))
```

```{r}
dat <- list(Y = df$discoveries, N = dim(df)[[1]])
```
# Fit model

done in another script

```{r}
lambda <- extract(fit,"lambda")[[1]]
```

# credible interval

```{r}
print(fit, probs = c(0.1,0.9))
```

```{r}
qplot(lambda)
```
```{r}
df %>% 
  ggplot(aes(discoveries))+
  geom_histogram()

df %>% 
  ggplot(aes(time, discoveries))+
  geom_point()
```
```{r}
library(tsibble)
library(feasts)
```
```{r}
df %>% 
  as_tsibble(index = time) %>% 
  ACF() %>% 
  autoplot()
```

